---
title: "shinyNotes"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{shinyNotes}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# shinyNotes
Shiny module for taking free-form notes and displaying them in a customizable UI.

The `shinyNotes` package provides an easy way to incorporate free-form note taking or discussion boards into your shiny application. The package includes a shiny module, `shinynotes`, that can be included in any shiny application to create a panel containing searchable, editable text broken down by section headers of your choice.

## Installation

Once released, you may install the stable version from CRAN, or the development version using `devtools`:
```{r setup, eval=FALSE}
# install from CRAN
install.packages('shinyNotes')

# or the development version, via devtools
devtools::install_github('danielkovtun/shinyNotes')
```

## Usage

#### Demo Shiny Application
To start off, try running a demo Shiny application included with the package by running:
```{r, eval=FALSE}
library(shinyNotes)
shinyNotes::runExample('demo')
```

#### Editing Notes
Notes can be directly modified by clicking the edit button and using the generated `textAreaInput` fields. To delete a note, simply remove all text from a `textAreaInput` and click save.

#### Adding Text Fields and Sections
You can add a new note to a section by clicking the "plus" button and selecting an existing category to add a note to. To add a new section header, fill in the inputs provided in the `modalDialog`. 

See the full documentation at https://danielkovtun.github.io/shinyNotes/. 
